%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Friggeri Resume/CV
% XeLaTeX Template
% Version 1.2 (3/5/15)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing

%\addbibresource{bibliography.bib} % Specify the bibliography file to include publications

\begin{document}

\header{Jonathan}{Chang}{} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
HOME:
1571 Via Campagna
San Jose, CA 95120
SCHOOL:
105 Lena St \#312
Ithaca, NY 14850
~
(408) 717-1539
~
\href{mailto:jpchang@cs.cornell.edu}{jpchang@cs.cornell.edu}
\href{https://github.com/jpwchang}{GitHub: jpwchang}
\section{technical skills}
\subsection{Programming}
\textbf{proficient in}
C, C++, C\#, Java, JavaScript, PHP, Python
\textbf{familiar with}
Dojo, HTML, Perl, Prolog, Racket, Ruby, Ruby on Rails, SQL
\subsection{Software}
Unity, Visual Studio, 3ds Max, MATLAB, Quartus
\subsection{Operating Systems}
Windows (client and server), Linux (Red Hat/Fedora, OpenSUSE, Arch), Android
\section{coursework}
Artificial Intelligence
Natural Language Processing
Computer Vision
Algorithms
Computability and Logic
Probability and Statistics
Core Lab - Image Processing
Autonomous Vehicles
Principles and Practice: Comp. Sci.
Data Structures \& Program Devel.
Computer Systems
Software Development
Programming Languages
Elec. \& Magnetic Circuits/Devices
Digital, Elec., \& Comp. Engineering
Discrete Mathematics
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{Expected 2023}
{PhD {\normalfont in Computer Science}}
{Cornell University, Ithaca, NY}

\entry
{May 2017}
{Bachelor {\normalfont of Computer Science}}
{Harvey Mudd College, Claremont, CA}
{Major GPA 3.9 \\ Dean's List: Spring/Fall 2014, Spring/Fall2015, Spring/Fall 2016, Spring 2017}

%------------------------------------------------

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Publications}

``Conversations Gone Awry: Detecting Early Signs of Conversational Failure''. Justine Zhang, \textbf{Jonathan P. Chang}, Cristian Danescu-Niculescu-Mizil, Lucas Dixon, Yiqing Hua, Nithum Thain, Dario Taraborelli. \emph{Proceedings of ACL} 2018. 

``Learning Representations of Emotional Speech with Deep
Convolutional Generative Adversarial Networks''. \textbf{Jonathan Chang} and
Stefan Scherer. \emph{IEEE ICASSP} 2017.

\vspace{0.1in}

\section{experience}

\subsection{Research Experience}

\begin{entrylist}

\entry
{6/18-Present}
{Cornell University}
{Ithaca, NY}
{\emph{Graduate Research Assistant}
\begin{itemize}
\item I work with Professor Cristian Danescu-Niculescu-Mizil on applying of natural language processing and machine learning to problems involving online interaction and conversation.
\end{itemize}}

\entry
{Summer 2016}
{University of Southern California}
{Los Angeles, CA}
{\emph{Summer Undergraduate Research Experience}
\begin{itemize}
\item Designed and evaluated a neural network for detecting emotional valence in human speech.
\end{itemize}}

\end{entrylist}

\subsection{Work Experience}

\begin{entrylist}

%------------------------------------------------

\entry
{Summer 2017}
{Proofpoint Inc.}
{Sunnyvale, CA}
{\emph{Software Engineering Intern}
\begin{itemize}
\item Developed a machine learning pipeline for quick filtering of suspicious URLs in emails
\end{itemize}}

\entry
{Summer 2015}
{Intentional Software Corporation}
{Bellevue, WA}
{\emph{Intern Software Analyst and Developer}
\begin{itemize}
\item Leveraged Intentional's application platform to create a unique color editor tool allowing users to manipulate 3d representations of color space
\end{itemize}}

\entry
{Summer 2014}
{Smith Micro Software}
{Santa Cruz, CA}
{\emph{Software Engineering Intern}
\begin{itemize}
\item Implemented a content browser for Poser Pro (Smith Micro's 3d animation tool) using JavaScript
and the Dojo toolkit
\item Added texture processing and multi-animation support to Poser Pro's FBX file format exporter using C++
\item Created a demo game using the Unity engine to demonstrate Poser Pro's Unity support
\end{itemize}}

%------------------------------------------------

\end{entrylist}

\pagebreak

\subsection{Leadership Experience}

\begin{entrylist}

\entry
{1/14--Present}
{Harvey Mudd College}
{Claremont, CA}
{\emph{Computer Science Grader/Tutor}
\begin{itemize}
\item Correct and grade homework assignments for Harvey Mudd Computer Science courses.
\item Provide assistance on homework and test preparation for Harvey Mudd Computer Science students.
\item Head grader/tutor for CS70 (Data Structures \& Program Development) for Fall 2015.
\end{itemize}}

%------------------------------------------------

\entry
{9/15--Present}
{Harvey Mudd College}
{Claremont, CA}
{\emph{Peer Academic Liaison}
\begin{itemize}
\item Connect Harvey Mudd students to academic resources and provide support, especially for first-year students
\end{itemize}}

%------------------------------------------------

\entry
{5/11--8/15}
{VirtualVEX Simulator Project}
{}
{\emph{Creator and Head Developer}
\begin{itemize}
\item Developed VirtualVEX, an open-source, customizable robotics simulator program using the Unity engine
\item Online at \href{https://sites.google.com/site/virtualvex/}{sites.google.com/site/virtualvex/}
\end{itemize}}

\end{entrylist}


\end{document}
